---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r}

# Read in activity file
step_DF <- read.csv(file="c:/coursera/ReproducibleData/week2/activity.csv",
                    sep = ",", header=TRUE)

# Convert character to Date Class
step_DF$date <- as.Date(step_DF$date , "%Y-%m-%d")
```
## What is mean total number of steps taken per day?
####For this assignment ignore the missing values.
1. Calculate total daily steps.
2. Make a histogram of the total number of daily steps.
3. Calculate the mean and median of daily steps.

```{r}
# Ignore missing values
step_DF_na.omit <- na.omit(step_DF)

# Aggregate steps as per date to get total number of steps in a day
dailySteps <- aggregate(steps ~ date, step_DF_na.omit, sum)

# Create histogram of total number of steps in a day
hist(dailySteps$steps, col=1, main="Total number of steps per day", xlab="Total number of steps in a day")

```

```{r}
# Calculate mean and median of steps per day
meanSteps <- mean(dailySteps$steps)
meanSteps

medianSteps <- median(dailySteps$steps)
medianSteps

cat("Daily Steps mean = ", meanSteps, "and median = ", medianSteps)
```
## What is the average daily activity pattern?
1. Make a time series plot (type = “l”) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).
2. Which 5-minute interval contains the maximum number of steps?

```{r}
# aggregate steps to get average daily interval
 internalSteps<- aggregate(steps ~ interval, step_DF_na.omit, mean)

# Plot daily average interval
plot(internalSteps$interval, internalSteps$steps, type='l', col=1, 
     main="Average number of Daily Steps", xlab="Interval", 
     ylab="Average number of steps")
```

```{r}
# Got lazy and just did which.max and max
maxSteps <- max(internalSteps$steps)
maxSteps

maxInternal <- which.max(internalSteps$steps)
maxInternal

cat("5-minute interval value = ", maxInternal, "and maximum steps = ", maxSteps)

```

## Imputing missing values
Note that there are a number of days/intervals where there are missing values (coded as NA). The presence of missing days may introduce bias into some calculations or summaries of the data.

1. Calculate the total number of missing values in the dataset.
2. Devise a strategy for filling in all of the missing values in the dataset.
3. Create a new dataset that is equal to the original dataset but with the missing data filled in.
4. Make a histogram of the total number of steps taken daily and Calculate the mean and median. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}
# get number of rows with NA's
stepCnt_NA <- sum(is.na(step_DF))

cat("The total number of NA's = ", stepCnt_NA)

```

```{r}
# Fill in missing values
# Will use the mean for like intervals to replace NA's.  
for (i in 1:nrow(step_DF))
  {
    if (is.na(step_DF$steps[i]))
      {
         rowNum <- which(internalSteps$interval == step_DF$interval[i])
         stepAvg <- round(internalSteps$steps[rowNum], digits=0)
         step_DF$steps[i] <- stepAvg
      }
  }

# Get total daily steps
dailyTotalSteps <- aggregate(steps ~ date, step_DF, sum)

# create histogram of total number of steps in a day
hist(dailyTotalSteps$steps, col=1,
    main="Total Daily Steps", xlab="Total Daily Steps")
```

```{r}
# Calculate mean and median of steps per day
meanTotalSteps <- mean(dailyTotalSteps$steps)
meanTotalSteps

medianTotalSteps <- median(dailyTotalSteps$steps)
medianTotalSteps

cat("Imputed: Daily Steps mean = ", meanTotalSteps, "and median = ", medianTotalSteps)
```


## Are there differences in activity patterns between weekdays and weekends?

