---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r}

# Read in activity file
step_DF <- read.csv(file="c:/coursera/ReproducibleData/week2/activity.csv",
                    sep = ",", header=TRUE)

# Convert character to Date Class
step_DF$date <- as.Date(step_DF$date , "%Y-%m-%d")
```
## What is mean total number of steps taken per day?
####For this assignment ignore the missing values.
1. Calculate total daily steps.
2. Make a histogram of the total number of daily steps.
3. Calculate the mean and median of daily steps.

```{r}
# Ignore missing values
step_DF_na.omit <- na.omit(step_DF)

# Aggregate steps as per date to get total number of steps in a day
dailySteps <- aggregate(steps ~ date, step_DF_na.omit, sum)

# Create histogram of total number of steps in a day
hist(dailySteps$steps, col=1, main="Total number of steps per day", xlab="Total number of steps in a day")

```
## Calculate mean and median of steps per day
```{r}
meanSteps <- mean(dailySteps$steps)
meanSteps

medianSteps <- median(dailySteps$steps)
medianSteps

cat("Daily Steps mean = ", meanSteps, "and median = ", medianSteps)
```
## What is the average daily activity pattern?
1. Make a time series plot (type = “l”) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).
2. Which 5-minute interval contains the maximum number of steps?

```{r}
# aggregate steps to get average daily interval
 internalSteps<- aggregate(steps ~ interval, step_DF_na.omit, mean)

# Plot daily average interval
plot(internalSteps$interval, internalSteps$steps, type='l', col=1, 
     main="Average number of Daily Steps", xlab="Interval", 
     ylab="Average number of steps")
```

```{r}
# Got lazy and just did which.max and max
maxSteps <- max(internalSteps$steps)
maxSteps

maxInternal <- which.max(internalSteps$steps)
maxInternal

cat("5-minute interval value = ", maxInternal, "and maximum steps = ", maxSteps)

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
