---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r}

# Read in activity file
step_DF <- read.csv(file="c:/coursera/ReproducibleData/week2/activity.csv",
                    sep = ",", header=TRUE)

# Convert character to Date Class
step_DF$date <- as.Date(step_DF$date , "%Y-%m-%d")
```
## What is mean total number of steps taken per day?
####For this assignment ignore the missing values.
1. Calculate total daily steps.
2. Make a histogram of the total number of daily steps.
3. Calculate the mean and median of daily steps.

```{r}
# Ignore missing values
step_DF_na.omit <- na.omit(step_DF)

# Aggregate steps as per date to get total number of steps in a day
DailySteps <- aggregate(steps ~ date, step_DF_na.omit, sum)

# Create histogram of total number of steps in a day
hist(DailySteps$steps, col=1, main="Total number of steps per day", 
     xlab="Total number of steps in a day")
```
## Calculate mean and median of steps per day
```{r}
mean(DailySteps$steps)
```
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
